\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{authblk}
\renewcommand\Authsep{, }
\renewcommand\Authands{ and }
\setlength{\affilsep}{0.6em}

\title{\textbf{Title Page}\\[0.5em]
Learning-Augmented Exact Optimization for Asymmetric Pick-and-Place Sequencing}
\date{}

\author[1]{Panav Arpit Raaj\thanks{Corresponding author. Email: \href{mailto:praajarpit@gmail.com}{praajarpit@gmail.com}. ORCID: \href{https://orcid.org/0009-0001-2476-756X}{0009-0001-2476-756X}. Present role: Robotics Engineer, Eternal.ag.}}
\author[1]{Atul Thakur\thanks{Email: \href{mailto:athakur@iitp.ac.in}{athakur@iitp.ac.in}. ORCID: \href{https://orcid.org/0000-0001-5937-4793}{0000-0001-5937-4793}}}
\affil[1]{BRAIn Lab, Department of Mechanical Engineering, Indian Institute of Technology Patna, Patna 801106, Bihar, India}

\begin{document}
\maketitle

\paragraph{Corresponding author.}
Panav Arpit Raaj, BRAIn Lab, Department of Mechanical Engineering, Indian Institute of Technology Patna, Patna 801106, Bihar, India. Email: \href{mailto:praajarpit@gmail.com}{praajarpit@gmail.com}.

\section*{Funding}
This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{CRediT authorship contribution statement}
\textbf{Panav Arpit Raaj:} Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Software, Validation, Visualization, Writing -- original draft, Writing -- review \& editing.
\textbf{Atul Thakur:} Conceptualization, Project administration, Supervision, Writing -- review \& editing.

\end{document}
